Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex
tweak

Our evaluation demonstrates the feasibility of building new service abstractions
atop programmable storage, focusing on the
performance of the internal
abstractions exposed by Malacology and
used to construct the Mantle and ZLog services. We also discuss
latent capabilities we discovered in this process that let us navigate
different trade-offs within the services themselves. First, we benchmark
scenarios 
%where contention is at the sequencer 
with high sequencer contention
by examining the interfaces used
to map ZLog onto Malacology; specifically, we describe the sequencer
implementation and the propagation of object and data interfaces interfaces.
Next, we benchmark scenarios in which the storage system manages multiple logs by using Mantle to
balance sequencers across a cluster.

>>>>

Our evaluation demonstrates the feasibility of building new service abstractions
atop programmable storage, focusing on the
performance of the internal
abstractions exposed by Malacology and
used to construct the Mantle and ZLog services. We also discuss
latent capabilities we discovered in this process that allow us---as well as future
storage system programmers---to navigate
different trade-offs within the services themselves. First, we benchmark
scenarios 
%where contention is at the sequencer 
with high sequencer contention
by examining the interfaces used
to map ZLog onto Malacology; specifically, we describe the sequencer
implementation and the propagation of object and data interfaces interfaces.
Next, we benchmark scenarios in which the storage system manages multiple logs by using Mantle to
balance sequencers across a cluster.
